Data Management for LSST Special Programs

### 2024-04-09 sec_intro.tex
fix user takeaway

\item There will be cases where User-Generated Processing is required to meet
science goals from Special Programs.
(Section~\ref{ssec:proc_user})

@@

User-Generated Processing for Special Programs data will be necessary in cases that
do not meet the conditions of "possible and necessary" as defined in
Section~\ref{ssec:sci_sproc} and further illustrated in Section~\ref{ssec:proc_special}.
This will include cases where the science goals require custom algorithms or software,
or computational capacities which are beyond the Rubin-provided
computational resources (Section~\ref{ssec:sci_comp}).

Further details such as Rubin-provided support for User-Generated Processing is discussed
in Section~\ref{ssec:proc_user}.

>>>>

\item There will be cases where User-Generated Processing is required to meet
science goals from Special Programs, and user processing will be supported with
computational resources.
(Section~\ref{ssec:sci_comp})

@@

User-Generated Processing for Special Programs data will be necessary in cases that
\emph{do not} meet the conditions of "possible and necessary" as defined in Section~\ref{ssec:sci_sproc}.
Computational tools, resources, and support will be provided by Rubin for User-Generated
Processing, as described in Section~\ref{ssec:sci_comp} and Section~\ref{ssec:proc_user}.

### 2024-04-09 sec_req.tex

\textbf{Latency requirements apply to alerts from Special Programs images. --}
It is a requirement that any Special Programs processing done with the 
Prompt pipeline (or a reconfigured version of it) is subject to the same 
timescales and latency constraints of 24 hours for the release of Prompt 
data products and 1 minute for the transmission of Alert packets 
(DMS-REQ-0344).

>>>>

\textbf{Latency requirements apply to alerts from Special Programs images. --}
It is a requirement that any Special Programs processing done with the 
Prompt pipeline is subject to the same 
timescales and latency constraints of 24 hours for the release of Prompt 
data products and 1 minute for the transmission of Alert packets 
(DMS-REQ-0344).
